A Decision Procedure for (Co)datatypes in SMT Solvers

### 2015-02-19 tex/body.tex
minor

Since by assumption $\Fc$ contains only equalities and disequalities, we have $\J \models \Fc$,
and since $\Fc$ is a superset of $\Ec$, we have that $\Ec$ is satisfied by $\J$.
\qed
\end{proof}

>>>>

Since by assumption $\Fc$ contains only equalities and disequalities, we have $\J \models \Fc$,
and since $\Ec \subseteq \Fc$,
% is a superset of $\Ec$,
we have that $\Ec$ is satisfied by $\J$.
\qed
\end{proof}
